# Linear Regression

Now we'll look at plain old OLS.  In STATA this is done using the command `reg`. In R, OLS is run using the command `lm()`. This is part of base-R, so there are no packages to install, you just start R and you're ready to go. 

While STATA seperates each part of the regression with a space, R wraps everything in parentheses. You don't have to include any spaces between the elements inside the pathenses, but it best to do so, for readability. You do have to add `~`, `+`, and/or `:`. `~` goes between the dependent variabale, and the rest of the equation, `+` seperates the rest of the variables in an additive model, and `:` indicates a multiplitcative interation. So 

```
gen x1x2 = x1*x2
reg y x1 x2 x1x2
``` 
in STATA. Is written

```lm(y ~ x1 + x2 + x1:x2, data = stata.data)```
In R.



This R code could also be written: 
```
lm(stata.data$y ~ stata.data$x1 + stata.data$x2 + 
    stata.data$x1:stata.data$x2)
```
And just to add even more variety, one could also write:
```
attach(stata.data)
lm(y ~ x1 + x2 + x1:x2)
```

## Which way should you write your model?
Starting with `attach(stata.data)` is likely to be most comfortable for STATA users. This method loads a single dataframe into the environment (in this case stata.data) and now any variable you reference is assumed to belong to that dataframe. If you call a variable that doesn't exist in the dataframe, you see the message `Error in eval(predvars, data, env) : object 'variable' not found` where `'variable'` is that name of the non-existant variable you tried to call. 

If you want to switch to another dataframe, you simply write `detach(stata.data)` and then attach another dataframe (i.e. `attach(stata.data2)`). Note that `detach()` will not remove the data from the environment, it only removes it from being the default for calling variables. If you want to remove the data from the environment, type `rm(stata.data)`.

While this may be the most similar to the way you're used to working with dataframes in STATA, one of the advantages of R is that you can work with various different dataframes at the same time. You can alsways indicate which dataframe a variable belongs to by writeing `dataframe$variable`. This is seen in the second example above and is quite specific, but requires specifying the dataframe for every variable. This can be tedious. Adding `data = dataframe` is a nice balance where you only have to specify the data once per model, but you can still access different dataframes without constantly typing `detach()` and `attach()`.  

## Viewing the results
If you simply run the `lm()` command without assigning it to an object, the results will print in the console. If you do assign you model to an object, you can access the results with the `summary()` command. Here's an example using the `ToothGrowth` dataset, which examines the role of vitimins in the rate of guinea pigs' tooth growth. 

```{r}
data("ToothGrowth")
dat <- data.frame(ToothGrowth)

model <- lm(len ~ supp + dose, data = dat)
summary(model)
```

You can combine the results of numerous models into a single (publication ready) table as we've seen before.

```{r}
library(modelsummary)

cn = c(
    "suppVC" = "Supplement Type",
    "dose" = "Dose (mg/day)"
)

modelsummary(models = model, coef_map = cn, stars = TRUE)
```
